\documentclass[onecolumn, draftclsnofoot,10pt, compsoc]{IEEEtran}
\usepackage{graphicx}
\usepackage{url}
\usepackage{setspace}
\usepackage{cite}
\usepackage{geometry}
\usepackage{enumitem}


\geometry{textheight=9.5in, textwidth=7in}

% 1. Fill in these details
\def \CapstoneTeamName{Audio Extravaganza}
\def \CapstoneTeamNumber{26}
\def \GroupMemberOne{Martin Barker}
\def \GroupMemberTwo{Devon Cash}
\def \GroupMemberThree{Alexander Niebur}
\def \GroupMemberFour{Mason Sidebottom}
\def \GroupMemberFive{Ben Windheim}
\def \CapstoneProjectName{Audio Extravaganza}
\def \CapstoneSponsorCompany{Oregon State University}
\def \CapstoneSponsorPerson{Kirsten Winters}

% 2. Uncomment the appropriate line below so that the document type works
\def \DocType{		
                %Problem Statement
				% Requirements Document
				Technology Review
				%Design Document
				%Progress Report
				}
			
\newcommand{\NameSigPair}[1]{\par
\makebox[2.75in][r]{#1} \hfil 	\makebox[3.25in]{\makebox[2.25in]{\hrulefill} \hfill		\makebox[.75in]{\hrulefill}}
\par\vspace{-12pt} \textit{\tiny\noindent
\makebox[2.75in]{} \hfil		\makebox[3.25in]{\makebox[2.25in][r]{Signature} \hfill	\makebox[.75in][r]{Date}}}}
% 3. If the document is not to be signed, uncomment the RENEWcommand below
\renewcommand{\NameSigPair}[1]{#1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{titlepage}
    \pagenumbering{gobble}
    \begin{singlespace}
        \hfill  
        \par\vspace{.2in}
        \centering
        \scshape{
            \huge CS Capstone \DocType \par
            {\large\today}\par
            \vspace{.5in}
            \textbf{\Huge\CapstoneProjectName}\par
            \vfill
            {\large Prepared for}\par
            \Huge \CapstoneSponsorCompany\par
            \vspace{5pt}
            {\Large\NameSigPair{\CapstoneSponsorPerson}\par}
            {\large Prepared by }\par
            Group\CapstoneTeamNumber\par
            % 5. comment out the line below this one if you do not wish to name your team
            \CapstoneTeamName\par 
            \vspace{5pt}
            {\Large
                % \NameSigPair{\GroupMemberOne}\par
                % \NameSigPair{\GroupMemberTwo}\par
                % \NameSigPair{\GroupMemberThree}\par
                \NameSigPair{\GroupMemberFour}\par
                % \NameSigPair{\GroupMemberFive}\par
            }
            \vspace{20pt}
        }
        \begin{abstract}
        %UNCOMMENT WHEN OTHER CITATIONS ARE ADDED
        % \cite{ph}
        % 6. Fill in your abstract    
        The Audio Extravaganza project aims to build a modulation and looping pedal that is affordable, intuitive, and effective.
        To do this, a variety of technologies will need to be selected and used in conjunction to create a functional product.
        This paper will evaluate three sets of technologies that will be crucial to the success of the project.
        Firstly, audio programming languages will be compared on their ability to integrate with other tools -- software and hardware --, portability, and ease of use on a single board computer.
        Secondly, process control approaches will be evaluated on syntax, speed, and support. 
        Finally, visual output devices will be compared on their cost, usability, and versatility.
        Each of these comparisons deliver a final recommendation on which specific option will provide the best result for the Audio Extravaganza team.
		
		\end{abstract}     
    \end{singlespace}
\end{titlepage}
\newpage
\pagenumbering{arabic}
\tableofcontents
% 7. uncomment this (if applicable). Consider adding a page break.
%\listoffigures
%\listoftables

% Uncomment to make table of contents full page
\clearpage
\section{Role}
For the remainder of the project, I will be taking the roles of: head of testing, head of code reviews, and software engineer.
For the role of head of testing, I will verify that our testing process is complete and robust enough to verify a refined product.
As for head of code reviews, I will verify that the source code created works as described, and meets organization style guidelines.
The role of software engineer will include writing code.
Aside from these roles, my other duties will include, but are not limited to: writing documentation, implementation, hardware implementation, user testing, etc.
Finally, this is not an exhaustive description of my duties in this project, but a generalized glance at what I will be responsible for.
\section{Background}
The Audio Extravaganza project is a unique effort to help create a useful tool for musicians.
There are a wide variety of barriers for creators and consumers alike in the music industry, ranging from financial means to technical expertise.
This project aims to help those who are interested in the creation of music be able to create unique sounds in an accessible format.
Our team proposes to build a modular effects pedal that users can interface with to generate unique sounds while cultivating a captivating experience.
To complete this task, our project will be divided into three main stages. Research, implementation, and embedding.
The success of our product will be contingent on the success each of these stages. 
\input{AudioSoftware.tex}
\input{ControlStructure.tex}
\input{ExternalInterfaces.tex}


\clearpage
\bibliographystyle{IEEEtran}
\bibliography{./refs.bib}

% 8. now you write!



\newpage

\end{document}
