% Alex
\section{Overview}

\subsection{Scope}
The Audio Extravaganza project is designed to bring an affordable audio effects solution to consumers at a competitive price. Our final product will be an embedded system with a variety of audio effects, I/O ports for audio signals, knobs to control the audio effects, and a metallic frame to house the system. The audio effects will be programmed and ran in the programming environments Supercollider and Pure Data on the BeagleBoard X15.

\subsection{Purpose}
This documentation is designed to describe the goals for the Audio Extravaganza project in a way that is easy to understand and maximizes coverage of the project objectives through observation of different viewpoints. Additionally, this document will allow our client to determine if our objectives correspond to the expectation set for the project.

\subsection{Intended Audience}
The following document is intended to be read by multiple parties:
\begin{itemize}
\item Kirsten Winters, our project client for review of project goals, expectations, and requirements.
\item Kevin McGrath, for project understanding and grading purposes.
\item Members of the Audio Extravaganza team, for use during the implementation portion of development alongside the case where a dispute about design decisions require reviewing our design choices.
\item Members of the testing team and end-users, for understanding about how to use our final product and for finding any issues that could arise within our design document.
\end{itemize}

\subsection{Conformance}
The following document shall conform to the standards and specifications set by our client, and in the case that any specification is not met, we shall modify our design to accommodate. In addition, the requirements document explains the manufacturing quality for which the implementation needs to conform to. Said document will be a reference for validation of implementation results. 